Time-series modeling of epidemics in complex populations: detecting changes in incidence volatility over time

### 2025-01-24 ms-3/ms.tex
Update ms.tex
Last of methods transfer

>>>>

\subsection*{Data availability and processing}

COVID-19 cumulative case data are from [The New York Times](https://github.com/nytimes/covid-19-data/) and county population sizes are from [The United States Census Bureau](https://www2.census.gov/programs-surveys/popest/datasets/2020-2021/counties/totals/. Cumulative cases for the largest three counties in each state were converted to weekly counts by keeping the last observation from each week and differenced to compute new cases. Note that missing values for new cases were all at the beginning of the pandemic and were imputed as zero. Apprxoimately 0.24% of new cases were negative due to corrections in the cumulative data. These were also imputed as zero.

\subsection*{Application to empirical data}

For each time step in each empirical epidemic curve, a series of \begin{math}\mu_t\end{math} and a single value of \begin{math}\theta\end{math} was estimated for the corresponding window. 
By moving the window one time step at a time, time series of \begin{math}\theta\end{math} estimates and p-values were produced. We investigated large counties (the three counties with the largest populations in each state).
